RDF Validation Requirements - Evaluation and Logical Underpinning

### 2014-12-23 paper/RDF validation requirements/RDF validation requirements.tex
DL mappings

\begin{ex}
# Individuals matching the ’:SuperJediMaster’ data shape
# ------------------------------------------------------
:Yoda 
\end{ex}
\er{Note that this example includes also has at-most restriction.}\\

@@

@@

\tb{ToDO: check DL}
\er{foaf: or xsd:string is no DL syntax. So you can delete 18.2 if you are fine.}
\begin{gcotable}
property & foaf:Person & hasName & - & xsd:string & $\geq$ & 2 \\
\end{gcotable}

@@

@@

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 resource
	\item Jedi masters are mentoring at least 1 and at most 2 resources
	\item Super Jedi masters are mentoring at least 3 resources  
\end{itemize}
\er{Notice that this example includes minimum restriction.}
\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

@@

\tb{ToDO: OWL 2 DL}
\er{why OWL 2 DL?}
\begin{ex}
# ShEx
# ----
:Jedi {
    :attitude ('good') }
:JediStudent {
    & :Jedi ,
    :studentOf @:Jedi{1} }
:JediMaster {
    & :Jedi ,
    :mentorOf @:Jedi{1,2} }
:SuperJediMaster {
    & :Jedi ,
    :mentorOf @:Jedi{3,} }
\end{ex}

>>>>

\begin{ex}
# Individuals matching the ’:SuperJediMaster’ data shape
# ------------------------------------------------------
:Yoda 
\end{ex}

@@

\textcolor{red}{corrections (to verify):}

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
$JediMasters \sqsubseteq Jedi \sqcap \geq1 studentOf^{-}.\top \sqcap \leq2 studentOf^{-}.\top $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 studentOf^{-}.\top $
\end{DL}

\begin{DL}
$Captain \sqsubseteq \geq1 commandsVessel.\top $
\end{DL}

\begin{gcotable}
property & Captain & commandsVessel & - & $\top$ & $\geq$ & 1 \\
\end{gcotable}

@@

\begin{gcotable}
property & foaf:Person & hasName & - & xsd:string & $\geq$ & 2 \\
\end{gcotable}

@@

\begin{DL}
$Captain \sqsubseteq \geq1 commandsVessel . Vessel $
\end{DL}

\begin{gcotable}
property & Captain & commandsVessel & - & Vessel & $\geq$ & 1 \\
\end{gcotable}

\begin{DL}
$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
\end{DL}

\begin{gcotable}
property & $\geq$1 commandsVessel . Vessel & commandsVessel & - & Vessel & $\geq$ & 1 \\
class & FederationCaptain & - & - & Federation, $\geq$1 commandsVessel . Vessel & $\sqcap$ & - \\
\end{gcotable}

@@

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 resource
	\item Jedi masters are mentoring at least 1 and at most 2 resources
	\item Super Jedi masters are mentoring at least 3 resources  
\end{itemize}
\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

@@
